### 2017-05-30 paper.tex
Clarify feedback for target audience

Pre- and post-class surveys also are essential in focusing in on the audience for a given lesson.
It can sometimes be difficult for lesson developers to understand the frame of a given learner
so surveys (particularly post-class surveys) can reveal hidden assumed knowledge
that can be expanded on or acknowledged.

>>>>

Pre- and post-class surveys also are essential in focusing in on the audience for a given lesson.
Refering back to Rule~1, it can sometimes be difficult for lesson developers to understand the frame of a given learner
so surveys (particularly post-class surveys) can reveal hidden assumed knowledge
that can be expanded on or acknowledged to refine the target audience.
